Pre/Post-Trikafta

### 2022-01-20 Christine Chan/Pre-post Trikafta/pre_post_trikafta.Rmd
Update pre_post_trikafta.Rmd
started piecewise regression

>>>>

# Spline regression

```{r}
a1c = read.csv("./Data_Raw/Data From CHCO/Copy of A1C and OGTTs Before and After Trikafta_cc modified 8.25.20.csv")
a1c$Earliest.Trikafta.Date.in.PortCF = mdy(a1c$Earliest.Trikafta.Date.in.PortCF)
a1c$Date.of.A1C.or.OGTT = mdy(a1c$Date.of.A1C.or.OGTT)
a1c = a1c %>% 
  mutate(time = as.numeric(difftime(Date.of.A1C.or.OGTT,
                                    Earliest.Trikafta.Date.in.PortCF,
                                    units = "days"))) %>%
  filter(!is.na(Hgb.A1C),abs(time)<=365)
a1c$spline = ifelse(a1c$time>0,1,0)
a1c$X = a1c$time * a1c$spline
# Segmented model, knot at 0
smod = lme(Hgb.A1C ~ time + X,random = ~1|MRN,data = a1c,na.action = na.omit)
# Plot
# Segments
xs1 = c(min(a1c$time),0)
beta1 = summary(smod)$tTable[1:2]
ys1 = cbind(1, xs1) %*% beta1

xs2 = c(0,max(a1c$time))
beta2 = c(summary(smod)$tTable[1],sum(summary(smod)$tTable[2:3]))
ys2 = cbind(1,xs2) %*% beta2

p = ggplot(a1c,aes(x = time,y = Hgb.A1C)) + 
  geom_point() + 
  geom_segment(aes(x = xs1[1], xend = xs1[2], y = ys1[1], yend = ys1[2]),color = "blue") +
  geom_segment(aes(x = xs2[1], xend = xs2[2], y = ys2[1], yend = ys2[2]),color = "blue") +
  xlab("Days from Trikafta Start") + ylab("HbA1c") + theme_bw()
p
```
